---
title: "Supply Chain assignment 2 - Rajshree Mishra (rm62528)"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

------------------------------------------------------------------------

<center>

## Assignment #2: ARIMA Laboratory

#### Due: Nov. 29 (Before Class)

#### (40 points)

</center>

------------------------------------------------------------------------

### Part I. Estimating Growth Potential and Capacity Utilization

Suppose you are working for a firm in the restaurant business looking
into the possibility of starting operations in Australia. Your company
has already narrowed its focus to five states: (i) Queensland, (ii)
Victoria, (iii) New South Wales, (iv) Western Australia, and (v) the
Australian Capital Territory. The decision of locations to start
operations depend on two factors:

(A) **Growth Potential:** More than the size of the market itself, the
    firm is interested in starting operations in locations with high
    growth rates. The reasoning behind this decision is that it is
    easier to gain a foothold in a market that is growing than in one
    that is stagnant.

(B) **Demand Variability:** There are two dimensions to demand
    variability. First, the change in mean demand from month to month
    over the year, i.e., the seasonality; and second, the volatility of
    the demand within each season. This is important as high levels of
    seasonality and high levels of uncertainty lead to reduced expected
    levels of capacity utilization and lower cash flows from operation.

To aid your analysis, we include in the code box below an ETS analysis
of the sales (turnover) of the aggregate restaurant industry in each
state. Please base your answers to question (1) and (2) on the results
obtained by the analysis below.

```{r warning=FALSE}
library(fpp3)

R <- aus_retail %>%
  filter(Industry == "Cafes, restaurants and takeaway food services", 
         State == "Australian Capital Territory"|
           State == "Queensland" |
           State == "Victoria" |
           State == "Western Australia" |
           State == "New South Wales" ) %>%
  mutate(Sales = Turnover) %>%
  select(State, Sales)

R %>% autoplot(.var = Sales)

m <- R %>% model(me = ETS(Sales))

MC <- m %>% components() 

MC %>% filter(State == "Australian Capital Territory") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Queensland") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "New South Wales") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Western Australia") %>% filter(Month >= ym("2017 Dec"))
MC %>% filter(State == "Victoria") %>% filter(Month >= ym("2017 Dec"))

MC %>% filter(State == "Australian Capital Territory") %>% autoplot()
MC %>% filter(State == "Queensland") %>% autoplot()
MC %>% filter(State == "New South Wales") %>% autoplot()
MC %>% filter(State == "Western Australia") %>% autoplot()
MC %>% filter(State == "Victoria") %>% autoplot()
```

1.  What is the type of growth estimated by the models above for each
    state?

**Answer** \n

The models above predict the following types of growth for each state:\n

a. Australian Capital Territory displays \<ETS(M,A,M)\> which
means additive trend growth. \n

b. New South Wales displays \<ETS(M,A,M)\>
which means additive trend growth. \n

c. Queensland displays
\<ETS(M,Ad,M)\> which indicates additive damped trend growth.\n

d.
Victoria displays \<ETS(M,Ad,M)\> which indicates additive damped trend
growth.\n

e. Western Australia displays \<ETS(M,A,M)\> which means
additive trend growth.




2. What are the values of the growth parameters (for each state) at the
    end of analysis period?

**Answer** \n

The growth parameter values for each state are listed
below as (level,slope):\n

Australian Capital Territory: (65.41453,
0.1681231) \n

Queensland: (709.3075, 0.11755319) \n

New South Wales:(1332.941,
3.468471)\n

Western Australia:(483.5807, 1.185602)\n

Victoria:(946.4926, 2.269460)

3.  What is the growth rate (expressed as a percentage) of sales
    experienced by each state over the last twelve months? Calculate
    this as the percent change in the de-seasonalized level of demand
    estimated over the last twelve months.

**Answer**\n

```{r}
cat(" Growth rate (expressed as a percentage) Australian Capital Territory: " , (65.41453	- 59.98852)*100/59.98852,'\n')
cat(" Growth rate (expressed as a percentage) Queensland: " , (709.3075	- 708.8852)*100/708.8852,'\n')
cat(" Growth rate (expressed as a percentage) New South Wales: " , (1332.941	- 1286.707)*100/1286.707,'\n')
cat(" Growth rate (expressed as a percentage) Western Australia: " , (483.5807	- 478.7444)*100/478.7444,'\n')
cat(" Growth rate (expressed as a percentage) Victoria: " , (946.4926	- 894.5664)*100/894.5664,'\n')
```

4.  One measure of operational risk is the effect of variability of mean
    demand from season to season on capacity utilization. A simple way
    to estimate this is to calculate for each of the five states
    $$D_{MAX} = \max_m D_m$$ where the index $m$ takes values
    corresponding to the last twelve months. That is, $D_{MAX}$ is the
    maximum mean level of demand fitted for the last twelve months. Then
    calculate the monthly metric of mean-forecast-based capacity
    utilization for each month as
    $$ U_m = \frac{D_m}{D_{MAX}} \times 100,$$ then, using the monthly
    mean-based capacity utilization obtain the average
    mean-forecast-based utilization as $$MU = mean(U_m)$$

Report the utilization calculation for each of the five states.
Summarize your analysis of sales growth potential and mean-variability
with a table indicating the annual growth rate and annual average
mean-base capacity utilization for each state. Management wants you to
pick three of these five states to start operations base only on your
analysis. explain your reasoning. Are there any states that are
dominated by other states based only on the growth vs. utilization
metrix? Explain.

**Answer**

```{r}
MC %>% filter(Month > ym("2017 Dec"))  -> Rolling_12_Month
Rolling_12_Month <- Rolling_12_Month  %>% mutate(Sales_fitted = Sales/ (1+remainder))
Rolling_12_Month <- Rolling_12_Month %>% group_by(State) %>% mutate(D_max_in_state = max(Sales_fitted))
Rolling_12_Month <- Rolling_12_Month  %>% mutate(Um_in_state = (Sales_fitted/D_max_in_state)*100)
Rolling_12_Month
```

```{r}
Rolling_12_Month_df <- data.frame(Rolling_12_Month) %>% dplyr::select(State, Um_in_state ) %>% group_by(State) %>% summarise(MU= mean(Um_in_state))
Rolling_12_Month_df<- Rolling_12_Month_df %>%  mutate(growth_rate=c(9.04,3.59,0.05,5.80,1.01))
Rolling_12_Month_df
```

I would advise the management to begin operations in the following
three places based on the examination of the mean-variability and 
potential for sales growth in the above table: \n

1. Australian Capital Territory: This state's growth rate is the highest
and its average utilization rate is 88.67, making it the most profitable.

2. Western Australia: This state may produce substantial profits if capacity
is used effectively, despite the fact that its growth rate is only 1.01 percent.
It has the greatest mean-utilization.

3. New South Wales: With a growth rate of 3.59, this state has the third-highest
growth rate overall, and its mean utilization is also higher than Victoria's.

Based only on growth rate, Western Australia has the highest capital usage,
whereas Australian Capital Territory has a growth rate of 9.04%.
I would advise against moving further with Queensland because of its extremely
low growth rate, or 0.05, and Victoria because of its extremely poor capacity
utilization because both factors could result in lower operating cash flows.

### Part II. Estimating Downside Risk in Capacity Utilization

After looking at your analysis and considering a number of additional
factors not included in your analysis, management decided to narrow
their prospecting to New South Wales, Western Australia and Victoria,
and are asking for a more detailed analysis of the capacity utilization
risk. To estimate this risk, they are asking you to use the actual
state-wide sales level as an index of what would be the company's sales,
and assume that the actual system capacity will be built as the 95%
quantile of the forecasted demand. Management is tasking you to estimate
the average capacity utilization and the downside capacity utilization
risk for each state. The following questions guide you through this
analysis:

5.  Using the training and testing sets specified below, fit the best
    ETS and ARIMA models for the sales in each of these three states.
    Comment on the selection of a forecasting model for each state based
    on the validity, accuracy and information criteria for each model.

**Answer**

```{r}
# Break into Training and Testing sets.

S <- R %>% 
  filter(State == "New South Wales" |
         State == "Western Australia" |
         State == "Victoria")

TR <- S %>% 
  filter(Month >= yearmonth("2000 Jan"),
         Month <= yearmonth("2017 Dec"))
TE <- S %>% 
  filter(Month >= yearmonth("2018 Jan"))


```

ETS Model fit ::

```{r}
mc_ETS <- TR %>%  model(m.auto = ETS(Sales))
mc_ETS %>% glance() 
```

```{r}
f_c_ETS <- mc_ETS %>% forecast(h=12)
rbind(mc_ETS %>% accuracy(), f_c_ETS %>% accuracy(data = TE))
```

"ETS(M,Ad,M)" is the best model that fits New South Wales, 
with AIC scores of 2595.304, 2656.059, and 2598.776. Since the
training and test sets' RMSEs are not significantly different from
one another, we may conclude that the model is not overfit. 
Similar to Victoria, Western Australia's best models for fitting 
data are ETS(M,Ad,M), and in both cases the models were not overfit
because the test and train scores for RMSE are not significantly different.
The model fit for Western Australia received very high accuracy scores,
indicating a very high level of model correctness.

ARIMA Model fit ::

```{r}

ARIMA_m_c <- TR %>%  model(ma = ARIMA(Sales))
ARIMA_m_c %>% glance() 

```

```{r}
ARIMA_f_c <- ARIMA_m_c %>% forecast(h=12)
rbind(ARIMA_m_c %>% accuracy(), ARIMA_f_c %>% accuracy(data = TE))
```

ARIMA(1,0,1)(1,1,1)[12] w/ drift is the model that fits New South Wales
the best. BIC is 1952.584, AIC is 1932.675, and AICc is 1933.101.
Similarily, ARIMA(1,0,1)(1,1,2)[12] w/ drift was the best model fit for
Victoria, and ARIMA(2,0,0)(0,1,2)[12] w/ drift was the best model match
for Western Australia. The RMSE score for Western Australia, however,
indicates that there may be overfit because the training RMSE is
much lower than the test RMSE.

After listening to your arguments, and considering other subjective
factors, your supervisor ask you to select the ARIMA model you obtained
for the states of Western Australia and Victoria, but she prefers the
ETS model for New South Whales. Use the above models to answer the
following questions.

6.  Fit the actual models selected as the best ARIMA and ETS (see above)
    and re-fit these models using all the available data (i.e, the **S**
    data set), and then prepare a 12-month ahead forecast for each
    state. Report the forecast and the 80% and 90% confidence intervals
    for each state.

**Answer**

According to supervisor recommendations, the models chosen for each state are:
Western Australia: ARIMA(2,0,0)(0,1,2)[12] w/ drift;
New South Wales: ETS(M,Ad,M); 
Victoria: ARIMA(1,0,1)(1,1,2)[12] w/ drift

For New South Wales, the forecast and the 80% and 90% confidence
ranges are as follows ::

```{r}
New_South_Wales_m_c <- S %>% filter(State == "New South Wales") %>%  model(m.NSW = ETS(Sales ~ error("M") + trend("Ad") + season("M")))
New_South_Wales_fc <- New_South_Wales_m_c %>% forecast(h=12) 
New_South_Wales_fc
```

```{r}
New_South_Wales_fc %>% hilo(level =c(80,90))%>%unpack_hilo("80%")%>%unpack_hilo("90%")
```

The prediction for Victoria and its 80% and 90% confidence intervals
are as follows ::

```{r}
Victoria_m_c <- S %>% filter(State == "Victoria") %>%  model(m.victoria = ARIMA(Sales ~ pdq(1,0,1) + PDQ(1,1,2)))
Victoria_fc <- Victoria_m_c %>% forecast(h=12) 
Victoria_fc
```

```{r}
Victoria_fc %>% hilo(level =c(80,90))%>%unpack_hilo("80%")%>%unpack_hilo("90%")
```

For Western Australia, the forecast and the 80% and 90% confidence
intervals are as follows ::

```{r}
Western_Australia_m_c <- S %>% filter(State == "Western Australia") %>%  model(m.wa = ARIMA(Sales ~ pdq(2,0,0) + PDQ(0,1,2)))
Western_Australia_fc <- Western_Australia_m_c %>% forecast(h=12) 
Western_Australia_fc
```

```{r}
Western_Australia_fc %>% hilo(level =c(80,90))%>%unpack_hilo("80%")%>%unpack_hilo("90%")
```

7.  Using the forecasting models in Question 6, assume that your company
    will build capacity up to 95% of the maximum demand forecast for the
    following 12 months. That is, $$CAP = \max_h D_{h,0.95}$$ , where
    $D_{h,0.95}$ is the maximum 95% quantile of the demand forecasts for
    the following 12 months. Then obtain the downside risk capacity
    utilization risk as $$ DUR_h = \frac{D_{h,0.05}}{CAP} \times 100, $$
    where $D_{h,0.05}$ is the demand corresponding to the 5% quantile of
    the sales forecast, and then, using the monthly downside capacity
    utilization $DUR_h$ obtain the average downside utilization as
    $$MDU = mean(DUR_h)$$

Report the utilization calculation for each of the three states.

**Answer**

Utilization Calculation of each state are given as follows:

```{r}
#CAP calculation
New_South_Wales_fc %>% mutate(CAP_temp = quantile(Sales, 0.95)) %>% mutate(CAP = max(CAP_temp)) -> New_South_Wales_gc
Western_Australia_fc %>% mutate(CAP_temp = quantile(Sales, 0.95)) %>% mutate(CAP = max(CAP_temp)) -> Western_Australia_gc
Victoria_fc %>% mutate(CAP_temp = quantile(Sales, 0.95)) %>% mutate(CAP = max(CAP_temp)) -> Victoria_gc


#DUR calculation
New_South_Wales_gc %>% mutate(DUR = (quantile(Sales, 0.05)/CAP)*100)  -> New_South_Wales_gc
Western_Australia_gc %>% mutate(DUR = (quantile(Sales, 0.05)/CAP)*100)   -> Western_Australia_gc
Victoria_gc %>% mutate(DUR = (quantile(Sales, 0.05)/CAP)*100)  -> Victoria_gc


#mean DUR calculation
New_South_Wales_gc %>% mutate(data.frame(New_South_Wales_gc) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR))) 
Western_Australia_gc %>% mutate(data.frame(Western_Australia_gc) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
Victoria_gc %>% mutate(data.frame(Victoria_gc) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))

```

8.  After examining your analysis in Question (7) management made two
    decisions: First, Building capacity up to the 95% quantile of demand
    was too considered too risky and affected expected profitability,
    and ask you to redefine the capacity at the 70% quantile as
    $$ CAP = \max_h D_{h,0.70}$$ and second, they decided that the
    downside risk at the 5% quantile was to conservative, and ask you to
    re-calculate the figures you reported using a downside demand
    estimated at the 10% quantile of the demand forecast and repeat your
    calculations in Question 7. Comment on the likely effect of the
    capacity reduction decision on the capacity utilization at the
    median demand (i.e., $D_{h,0.50}$) Explain the difference with the
    utilization quantities estimated in Question (4)
    
**Answer**

```{r}

#CAP calculation
New_South_Wales_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> New_South_Wales_gc2
Western_Australia_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> Western_Australia_gc2
Victoria_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> Victoria_gc2


#DUR calculation
New_South_Wales_gc2 %>% mutate(DUR = (quantile(Sales, 0.10)/CAP)*100)  -> New_South_Wales_gc2
Western_Australia_gc2 %>% mutate(DUR = (quantile(Sales, 0.10)/CAP)*100)   -> Western_Australia_gc2
Victoria_gc2 %>% mutate(DUR = (quantile(Sales, 0.10)/CAP)*100)  -> Victoria_gc2

#mean DUR calculation
New_South_Wales_gc2 %>% mutate(data.frame(New_South_Wales_gc2) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR))) 
Western_Australia_gc2 %>% mutate(data.frame(Western_Australia_gc2) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
Victoria_gc2 %>% mutate(data.frame(Victoria_gc2) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
```

```{r}

#CAP calculation
New_South_Wales_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> New_South_Wales_gc3
Western_Australia_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> Western_Australia_gc3
Victoria_fc %>% mutate(CAP_temp = quantile(Sales, 0.70)) %>% mutate(CAP = max(CAP_temp)) -> Victoria_gc3


#DUR calculation
New_South_Wales_gc3 %>% mutate(DUR = (quantile(Sales, 0.50)/CAP)*100)  -> New_South_Wales_gc3
Western_Australia_gc3 %>% mutate(DUR = (quantile(Sales, 0.50)/CAP)*100)   -> Western_Australia_gc3
Victoria_gc3 %>% mutate(DUR = (quantile(Sales, 0.50)/CAP)*100)  -> Victoria_gc3

#mean DUR calculation
New_South_Wales_gc3 %>% mutate(data.frame(New_South_Wales_gc3) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
Western_Australia_gc3 %>% mutate(data.frame(Western_Australia_gc3) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
Victoria_gc3 %>% mutate(data.frame(Victoria_gc3) %>% dplyr::select(State, DUR ) %>% summarise(mean_DUR= mean(DUR)))
```

Case 1 : Taking into account capacity expansion up to 95% of the maximum
demand anticipated for the upcoming 12 months with a 5% downside risk,
we obtained the numbers shown below: 

1. Victoria : Cap as 1138.357 \| mean_DUR as 81.10831 

2. New South Wales: Cap as 1822.508 \| mean_DUR as 64.16464 

3. Western Australia: Cap as 559.5504 \| mean_DUR as 82.95008

Case 2 :  The following figures were obtained after developing capacity
up to 70% of the maximum demand anticipated for the upcoming 12 months
with a 10% downside risk:

1. Victoria : Cap as 1100.953 \| mean_DUR as 84.74369

2. New South Wales: Cap as 1630.768 \| mean_DUR as 74.09598

3. Western Australia: Cap as 538.3846 \| mean_DUR as 87.18319

Case 3 :  The following numbers were obtained by considering capacity
expansion up to 70% of the maximum demand anticipated for the upcoming
12 months with a 50% downside risk. 

1. Victoria : Cap as 1100.953 \| mean_DUR as 87.84697

2. New South Wales: Cap as 1630.768 \| mean_DUR as 82.51651

3. Western Australia: Cap as 538.3846 \| mean_DUR as 90.61206


As a result of our assumption that capacity would be retained at 95%
and downside risk at 5%, we can observe in Case 1 that usage is below 90%
in every state.

Cases 2 and 3 demonstrate increased capacity use as the downside risk is raised
while maintaining the capacity at a constant 70%., for example for
New South Wales the mean_DUR went up from 74.09 to 82.51.

Following are the values we determined from Question 4: 

1. Victoria 84.36851

2. New South Wales 86.75189

3. Western Australia 90.64272

Instead of just some x%, we are fully evaluating the capacity in question 4.
While Victoria's capacity usage was better with 70% of the capacity held with
50% as a negative risk, we can see that New South Wales and Western Australia's
capacity utilization is better than any of the situations covered above.

